### 2018-11-07 report-gweil.tex
Add paragraph on the Theta function.

>>>>

There is yet another analogous example that might be of interest. Consider the theta function
$$ \Theta(t) := \sum_{n \in \mathbb{Z}} e^{-\pi n^2 t}   $$
It is well known that we have
$$ \Theta(\frac{1}{t}) =  t^{\frac{1}{2}} \Theta(t)   $$
and this functional equation implies the global functional equation for the Riemann zeta function. Is there an underlying object here which has Euler characteristic $\frac{1}{2}$??
Reference: \url{http://math.mit.edu/~poonen/786/notes.pdf}, see page 3 where this functional equation is stated as true for all positive real $t$.
